---
title: "Topic_Modelling"
output: github_document
---

## Dating - App Reviews Dataset
**Data Set** The data is from 2017-2022. I acquired the data using googleplayscraper from google playstore online. The data I received was more than just the column shown here but were unnecessary.


## Loading required packages
```{r}
library(readtext)
library(tidyverse)
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textstats)
library(quanteda.textplots)
library(textrank)
library(readtext)
library(udpipe)
library(dplyr)
library(topicmodels)
library(quanteda)
library(tidyverse)
library(tidytext)
library(topicdoc)
library(LDAvis)
library(broom)
library(ldatuning)
library(stm)
library(seededlda)
library(keyATM)
library(kableExtra)
```


## Describe data 
```{r}
Dating_df <- readtext::readtext("Assignment2.csv",text_field = "Review", docid_field = "ID")
glimpse(Dating_df)
```


## Create corpus
```{r}
Dating_corp <- corpus(Dating_df)
summary(Dating_corp, n = 5)
```


## Token and DCM
```{r}
Dating_toks <- tokens(
  Dating_corp,
  remove_punct = TRUE,
  remove_numbers = TRUE,
  remove_symbols = TRUE,
  remove_url = TRUE,
  split_hyphens = FALSE)

myStopWords = c("Where", "when", "shall", "include", "including", "by",
                "includes", "included", "may", "uses", "using", "used", "may",
                "also", "can", "whether", "so", "however", "rather", "â", "s",
                "said", "one", "two", "three", "k")

Dating_toks2 <- tokens_remove(
  Dating_toks, pattern = c(stopwords("en"), myStopWords))
```


## Feature Matrix

```{r}
Dating_dfm <- dfm(Dating_toks2)
Dating_dfm

Dating_dfm <- dfm(Dating_toks2, tolower = TRUE) %>%
  dfm_trim(min_termfreq = 3, min_docfreq = 10)

Dating_dfm

```

## Top Features 

```{r}
ndoc(Dating_dfm)

nfeat(Dating_dfm)

topfeatures(Dating_dfm, 30)


```

## 3 Relevent Keywords
```{r}
keyword1 <- kwic(Dating_toks2, pattern = phrase("learn*"), window = 2)
head(keyword1, 5)

keyword2 <- kwic(Dating_toks2, pattern = phrase("content*"), window = 2)
head(keyword2, 5)

keyword3 <- kwic(Dating_toks2, pattern = phrase("course*"), window = 2)
head(keyword3, 5)

head(keyword1, 5) %>%
  kbl() %>%
  kable_classic(bootstrap_options = "striped", full_width = F, position = "left")

```
```{r}
head(keyword2, 5) %>%
  kbl() %>%
  kable_classic(bootstrap_options = "striped", full_width = F, position = "left")

```
```{r}

head(keyword3, 5) %>%
  kbl() %>%
  kable_classic(bootstrap_options = "striped", full_width = F, position = "left")
```
```{r}
Dating_dfm_small <- dfm_trim(Dating_dfm, min_termfreq = 100)
nfeat(Dating_dfm_small)

Dating_fcm <- fcm(Dating_dfm_small)

feat <- names(topfeatures(Dating_fcm, 30))
fcmat_select <- fcm_select(Dating_fcm, pattern = feat, selection = "keep")
```

## Plot 
```{r}
size <- log(colSums(dfm_select(Dating_fcm, feat, selection = "keep")))

set.seed(123)


textplot_network(fcmat_select, min_freq = 0.5, edge_size = 2, edge_color = "red",
                 vertex_size = size/max(size)*3)

```

## LDA

```{r}
Dating_dtmat = quanteda::convert(Dating_dfm, to="topicmodels")
Dating_lda5 <- LDA(Dating_dtmat, k = 5, control = list(seed = 123))

```


## Top 5 

```{r}
Dating_lda5_betas <- broom::tidy(Dating_lda5)


top_terms_in_topics <- Dating_lda5_betas %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)


top_terms_in_topics

top_terms_in_topics %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()


test = subset(Dating_df)
nrow(test)

```

## Best number

```{r}
train_Dating_dtmat <- corpus_subset(Dating_corp)[1:600,]%>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbols = TRUE, remove_url = TRUE) %>%
  dfm(tolower = TRUE) %>%
  dfm_remove(c(stopwords("en"), myStopWords)) %>%
  dfm_trim(min_termfreq = 5, min_docfreq = 10) %>%
  quanteda::convert(to="topicmodels")

test_Dating_dtmat <- corpus_subset(Dating_corp)[601:1000,] %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbols = TRUE, remove_url = TRUE) %>%
  dfm(tolower = TRUE) %>%
  dfm_remove(c(stopwords("en"), myStopWords)) %>%
  dfm_trim(min_termfreq = 5, min_docfreq = 10) %>%
  quanteda::convert(to="topicmodels")

train_Dating_lda5 <- LDA(test_Dating_dtmat, k = 5, control = list(seed = 123))
perplexity(train_Dating_lda5, test_Dating_dtmat)


```

```{r}
n_topics_vec = 2:5
perplexity_vec = map_dbl(n_topics_vec, function(kk) {
  message(kk)
  train_Dating_ldaK <- LDA(train_Dating_dtmat, k = kk, control = list(seed = 123))
  perp = perplexity(train_Dating_ldaK, test_Dating_dtmat)
})
lda_perplexity_result = tibble(
  n_topics = n_topics_vec, perplexity = perplexity_vec
)
plot(lda_perplexity_result, type="l")

```
*Observation: As per the above perplexity 2 topics would be best number*

## LDA Tuning 
```{r}
library(ldatuning)
lda_ldatuning_result <- FindTopicsNumber(
  Dating_dtmat, topics = n_topics_vec,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "VEM", control = list(seed = 123), mc.cores = 4L, verbose = TRUE
)


FindTopicsNumber_plot(lda_ldatuning_result)



```
**Observation: As per the measures, 5 would be best number of topics**

```{r}
Dating_lda3 <- LDA(Dating_dtmat, k = 3, control = list(seed = 123))
topicdoc_result = topic_diagnostics(Dating_lda3, Dating_dtmat)
#below is the diagnostics for the best Model:
head(topicdoc_result, 5) %>%
  kbl() %>%
  kable_classic(bootstrap_options = "striped", full_width = F, position = "left")
```
## STM
```{r}
library(stm)
stm_Datingdfmat <- quanteda::convert(Dating_dfm, to = "stm")

out <- prepDocuments( stm_Datingdfmat$documents, 
                      stm_Datingdfmat$vocab, 
                      stm_Datingdfmat$meta)


Dating_tmob_stm <- stm(out$documents, out$vocab,K=5,
                         seed=123,emtol=1e-3, max.em.its=150)


toLDAvis(mod=Dating_tmob_stm, docs=out$documents)



plot(Dating_tmob_stm, type="summary", n=5)

```


## Top Quality
```{r}
topicQuality(Dating_tmob_stm, out$documents)
```

**Semantic coherence**It explains the relationship between words to aid understanding and interpretation of spoken and written language.

**Exclusivity** measures how distinctive the top words are to that topic

**Topic 3** has more semantic coherence and **Topic 1** has high value of exclusivity
## 4 set of keywords

```{r}
library(keyATM)
keyATM_docs <- keyATM_read(texts = Dating_dfm)
summary(keyATM_docs)



Dating_key_list = list(
  good = c("match", "reason", "amazing", "good", "amazing"),
  bad = c("banned", "fake", "terrible", "sucks", "useless"),
  timestamp = c("hours","times","every","work","subscription"),
  profile =c("tinder","profile","women","experience","men","erotic")
)
```


## Top 5 keyword in each topic 
```{r}
Dating_key_viz <- visualize_keywords(docs = keyATM_docs, keywords = Dating_key_list)
Dating_key_viz


Dating_tmod_keyatm_base <- keyATM(
  docs = keyATM_docs, 
  no_keyword_topics = 3, 
  keywords = Dating_key_list, 
  model = "base", 
  options = list(seed = 123))

top_words(Dating_tmod_keyatm_base, 5)

kable(top_words(Dating_tmod_keyatm_base, 5), caption = "Top 5 keywords")
```

